Adaptive Video Streaming with Optimized Bitstream Extraction and PID-based Quality Control

### 2016-01-12 response-r2.txt

Response to the reviewer comments of Paper MM-006412-R1: Adaptive Video Streaming with Optimized Bitstream Extraction and PID-based Quality Control by Shengbin Meng, Jun Sun, Yizhou Duan and Zongming Guo.

We would like to thank the reviewers for their help to make this paper better. We would also like to thank the associate editor for coordinating the review process. We have read the reviewer comments carefully, and tried to follow the suggestions as closely as possible. In this revision, we have also used a professional editing service to help refine and polish this paper regarding English usage.

Reviewer: 1

The reviewer is happy with the revised version of the paper and the authors¡¯ response to the reviewer¡¯s comments. The reviewer would recommend the paper to be accepted with minor corrections as listed below.

1. The reviewer is still not able to access the website (www.7dlive.com) which was mentioned in the abstract of the paper. The reviewer would suggest the authors double check the website¡¯s stability and accessibility. If the work¡¯s practical effectiveness (the suggested website to demo the proposed adaptive video streaming system) could not be checked or verified by others, the reviewer would suggest the authors remove this part of claim in the abstract and/or in the body of the paper.

Response:

In this revision, we have followed the suggestion and removed the claims about the website from this paper.

2. Typos, e.g. Table II, caption, the proposed algorith => algorithm

In future submission for a revised paper, it would be better if the authors can mark out the part of contents which are updated/added in response to reviewers¡¯ comments.

Response:

We have used a professional editing service to polish the language of this paper so that grammar flaws and typos (including the mentioned one) are corrected.

This revision includes many small updates about language usage as a result of the editing service, so it may be not appropriate to mark them in this response. We will follow your suggestion in future submission for a revised paper.

Thank you very much.

Reviewer: 2

The authors have successfully addressed all the comments I raised previously. I appreciate their efforts on the revision, and do not have any further comments.

Response:

Thank you very much.

Reviewer: 3

The authors have modified most of the parts mentioned in the first review. And the demonstration is satisfactory. The authors still need to discuss more on the robustness of the PID controller. Since the bandwidth fluctuation in the simulation is from 400kbps to 1400kbps, which is quite limited, the influence of large variance is not clear. The authors may need to do simulation on larger variance.

Response:

The values (400kbps, 1400kbps, etc.) in our simulation are average/mean values around which the bandwidth fluctuates, rather than the lower or upper bounds. The actual bandwidth can reach a value lower than 400kbps or higher than 1400kbps during the fluctuation. Therefore, the covered bandwidth range is actually larger than [400, 1400]. Robustness and performance of the proposed algorithm are verified in this range. More simulations/experiments can be performed to check the extreme cases in the future work. In this revision, we have added clarifications about the bandwidth fluctuation range (see second paragraph of Section V-B), and more discussion on the robustness of the PID controller (see last paragraph of Section IV-D).

Thank you very much.

### 2016-01-13 response-r2.txt

Response to the reviewer comments of Paper MM-006412-R1: Adaptive Video Streaming with Optimized Bitstream Extraction and PID-based Quality Control by Shengbin Meng, Jun Sun, Yizhou Duan and Zongming Guo.

We would like to thank the reviewers for their help to make this paper better. We would also like to thank the associate editor for coordinating the review process. We have read the reviewer comments carefully, and tried to follow the suggestions as closely as possible. In this revision, we have also used a professional editing service to help refine and polish this paper regarding English usage (receipt from the editing service is attached).

@@

2. Typos, e.g. Table II, caption, the proposed algorith => algorithm

In future submission for a revised paper, it would be better if the authors can mark out the part of contents which are updated/added in response to reviewers¡¯ comments.

Response:

We have used a professional editing service to polish this paper so that grammar flaws and typos (including the mentioned one) are corrected.

### 2016-02-23 tmm.tex
Make the figures appear in order
Prepare for final submission
Final single column

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option 
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
%\documentclass[journal,draftclsnofoot,onecolumn]{IEEEtran}
\documentclass[journal]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

@@

% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
\author{Shengbin~Meng, Jun~Sun, {\em Member, IEEE}, Yizhou~Duan and Zongming~Guo, {\em Member, IEEE} % <-this % stops a space
\thanks{Manuscript received July 15, 2015; revised December 3, 2015 and January 12, 2016. This work was supported by  National Key Technology R\&D Program of China under Grant 2015AA011605 and National Natural Science Foundation of China under contract No. 61271020.}
\thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
, 100080, China (email: mengshengbin@pku.edu.cn, sunjun@pku.edu.cn, duanyizhou@pku.edu.cn, guozongming@pku.edu.cn). Jun Sun and Zongming Guo are also with the Cooperative Medianet Innovation Center, Shanghai, 200240, China. Jun Sun is the corresponding author.}}

@@

\begin{figure}[h]
\centering
\includegraphics[width = 0.9\linewidth]{GOP-Structure.png}
\caption{Group of pictures (GOP) in SVC \label{fig:GOP_Structure}}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width = 0.9\linewidth]{ModelVerification.png}
\caption{Comparison of the actual and the estimated distortion for sequence {\em Foreman} \label{fig:model_verification}}
\end{figure}

@@

\begin{figure*}[t]
\centering
\subfloat[City]{
\includegraphics[width=0.42\textwidth]{City.jpg}
\label{fig:City}}
\subfloat[Foreman]{
\includegraphics[width=0.42\textwidth]{Foreman.jpg}
\label{fig:Foreman}}
\qquad
\subfloat[Harbour]{
\includegraphics[width=0.42\textwidth]{Harbour.jpg}
\label{fig:Harbour}}
\subfloat[Soccer]{
\includegraphics[width=0.42\textwidth]{Soccer.jpg}
\label{fig:Soccer}}
\caption{Performance of three bitstream extraction methods for various CIF sequences}
\label{fig:extraction-performance}
\end{figure*}

@@

@@

\begin{figure*}[t]
\centering
\subfloat[Average quality level of different control algorithms]{
\includegraphics[width=0.42\textwidth]{Quality-all.png}
\label{fig:quality-all}}
\subfloat[Quality level variance of different control algorithms]{
\includegraphics[width=0.42\textwidth]{Variance-all.png}
\label{fig:variance-all}}
\caption{Comparison of the long/short time prediction and the PDF algorithm in DSS}
\label{fig:performance-all}
\end{figure*}

\begin{figure*}[t]
\centering
\subfloat[Average quality level of the PID and PDF control algorithms]{
\includegraphics[width=0.42\textwidth]{Quality-two.png}
\label{fig:quality-two}}
\subfloat[Quality level variance of the PID and PDF control algorithms]{
\includegraphics[width=0.42\textwidth]{Variance-two.png}
\label{fig:variance-two}}
\caption{Comparison of the proposed PID algorithm and the PDF algorithm in DDS}
\label{fig:performance-two}
\end{figure*}

\begin{figure}
\centering
\includegraphics[width = 0.9\linewidth]{Fluctuation.png}
\caption{Video quality fluctuation with time \label{fig:fluctuation}}
\end{figure}

>>>>

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option 
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[journal,draftclsnofoot,onecolumn]{IEEEtran}
%\documentclass[journal]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

@@

% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
\author{Shengbin~Meng, Jun~Sun, {\em Member, IEEE}, Yizhou~Duan and Zongming~Guo, {\em Member, IEEE} % <-this % stops a space
\thanks{Manuscript received July 15, 2015; revised December 3, 2015 and January 12, 2016; accepted February 21, 2016. This work was supported by  National Key Technology R\&D Program of China under Grant 2015AA011605 and National Natural Science Foundation of China under contract No. 61271020.}
\thanks{Copyright (c) 2013 IEEE. Personal use of this material is permitted. However, permission to use this material for any other purposes must be obtained from the IEEE by sending a request to pubs-permissions@ieee.org.}
\thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
, 100080, China (email: mengshengbin@pku.edu.cn, sunjun@pku.edu.cn, duanyizhou@pku.edu.cn, guozongming@pku.edu.cn). Jun Sun and Zongming Guo are also with the Cooperative Medianet Innovation Center, Shanghai, 200240, China. Jun Sun is the corresponding author.}
}

@@

\begin{figure}[h]
\centering
\includegraphics[width = 0.8\linewidth]{GOP-Structure.png}
\caption{Group of pictures (GOP) in SVC \label{fig:GOP_Structure}}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width = 0.8\linewidth]{ModelVerification.png}
\caption{Comparison of the actual and the estimated distortion for sequence {\em Foreman} \label{fig:model_verification}}
\end{figure}

@@

\begin{figure*}[t]
\centering
\subfloat[City]{
\includegraphics[width=0.40\textwidth]{City.jpg}
\label{fig:City}}
\subfloat[Foreman]{
\includegraphics[width=0.40\textwidth]{Foreman.jpg}
\label{fig:Foreman}}
\qquad
\subfloat[Harbour]{
\includegraphics[width=0.40\textwidth]{Harbour.jpg}
\label{fig:Harbour}}
\subfloat[Soccer]{
\includegraphics[width=0.40\textwidth]{Soccer.jpg}
\label{fig:Soccer}}
\caption{Performance of three bitstream extraction methods for various CIF sequences}
\label{fig:extraction-performance}
\end{figure*}

@@

\begin{figure*}[t]
\centering
\subfloat[Average quality level of different control algorithms]{
\includegraphics[width=0.40\textwidth]{Quality-all.png}
\label{fig:quality-all}}
\subfloat[Quality level variance of different control algorithms]{
\includegraphics[width=0.40\textwidth]{Variance-all.png}
\label{fig:variance-all}}
\caption{Comparison of the long/short time prediction and the PDF algorithm in DSS}
\label{fig:performance-all}
\end{figure*}

\begin{figure*}[t]
\centering
\subfloat[Average quality level of the PID and PDF control algorithms]{
\includegraphics[width=0.40\textwidth]{Quality-two.png}
\label{fig:quality-two}}
\subfloat[Quality level variance of the PID and PDF control algorithms]{
\includegraphics[width=0.40\textwidth]{Variance-two.png}
\label{fig:variance-two}}
\caption{Comparison of the proposed PID algorithm and the PDF algorithm in DDS}
\label{fig:performance-two}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width = 0.8\linewidth]{Fluctuation.png}
\caption{Video quality fluctuation with time \label{fig:fluctuation}}
\end{figure}
